Binary companions of red giant stars with APOGEE DR14

### 2018-02-22 paper/1-catalog/twoface-catalog.tex
trivialities
adjust numbers to reflect new run.
troup figures

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{98,758}
\newcommand{\nvisits}{388,196}

@@

\title{Binary companions of red giant stars with APOGEE: \\
       catalog and companions that survive the common envelope}

@@

Less is known about uninteracting or detached companions to evolved stars.
Such systems are interesting because they enable studying extreme outcomes or
conditions of star formation and multiplicity.
For example, evolved stars are typically much brighter than their MS
counterparts, which enables characterizing the stellar companion population
throughout the Galactic disk over a wide range of chemical abundances.
They also provide a means to study the outcomes of stellar engulfment or
common-envelope evolution: Do short-period companions exist around evolved
stars, and do their statistics constrain stellar evolution on the red giant
branch (RGB)?
\todo{motivate time-domain spectroscopy}

@@

\subsection{Differences in companions of RC and RGB stars}
\label{sec:rc-rgb}

\subsection{Trends in RGB companions with chemical abundances}
\label{sec:rgb-chemistry}

@@

@@

\facility{\sdssiii, \apogee}

>>>>

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}

@@

\title{Binary companions of red giant stars with APOGEE DR14}

@@

Less is known about non-interacting or detached companions to evolved stars.
Such systems are interesting because they enable studying extreme outcomes or
conditions of star formation and multiplicity.
For example, evolved stars are typically much brighter than their MS
counterparts, which enables characterizing the stellar companion population
throughout the Galactic disk over a wide range of chemical abundances.
They also provide a means to study the outcomes of stellar engulfment or
common-envelope evolution: Do short-period companions exist around evolved
stars, and do their statistics constrain stellar evolution on the red giant
branch (RGB)?
\todo{motivate time-domain spectroscopy}

@@

@@

\subsection{Comparison to previous work} \label{sec:compare-troup}

Stuff.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{unimodal.pdf}
\end{center}
\caption{%
\label{fig:troup-unimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{multimodal.pdf}
\end{center}
\caption{%
\label{fig:troup-multimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{data-changed.pdf}
\end{center}
\caption{%
\label{fig:troup-datachanged}
}
\end{figure}

@@

\facility{\sdssiv, \apogee}
